\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for the horizontal lines, change thickness here

\begin{document}
\input{Titlepage.tex}

\tableofcontents

\section{Abstract}
EpisodeGuide is a web application that help users keep up to date on their favourite TV-shows. Both registered users and non-registered users can use this application, though registered users will get more features.
\\\\
Features include, but are not limited to:
\begin{itemize}
  \item Find new TV Shows.
  \item Keep track of episodes watched so far.
  \item Share TV Shows and episode data on social media (e.g Facebook).
  \item Login via Facebook, Twitter, Google etc.
  \item ... And more
\end{itemize}
What separates this application from all the others is simplicity. This was the main goal when we started developing EpisodeGuide, and is something we believe our users will benefit from in the long run.
Both end users and developers should be able to use and further develop EpisodeGuide in the future without going through several hundred pages of complicated documentation.
\\\\
EpisodeGuide uses different APIs, technologies and frameworks to accomplish this task.\\\\
APIs and frameworks:
\begin{itemize}
  \item TvDb for data about new and existing TV-shows and episodes
  \item Foundation as a framework for layout, box models etc.
  \item OpenSubtitles for subtitles
\end{itemize}
Technologies:
\begin{itemize}
  \item PHP
  \item MySQL
  \item Javascript
\end{itemize}
It is worth mentioning that EpisodeGuide is an application in developement. This means that at this stage, some features are currently not available or implemented.\\
\\
Since all the developers on our team believe that OpenSource is the best way to release and distribute new applications, EpisodeGuide will be OpenSource and available on Github for download once it is ready for a public release.
\\
\\
You can test EpisodeGuide live at: http://flawedlogic.pw/flawedlogic/bugfree-shame/
\section{Overview}
\subsection{Database}
\include{database}

\include{Workload}
\end{document}
