

\subsection{Week 1}
The project startet off with a meeting. After about two hours of brainstorming we had a couple of ideas of what we could do. We then gave ourself until the next day to think about the alternatives. \\
The next day we discussed wich of the ideas would be the most appropriate for our combined skill level and the time we had. After a little while, we came to the conclusion that making a website that holds information about tv-shows would be both challenching and interesting.\\

The rest of the week was spent on casually brainstorming ideas about the website and writing them down.
...
\subsection{Week 2}

The beginning of week 2 on spent on discussing exactly what kind of functionality we wanted and what tasks that had to be done, and in what order.
After we had a clear overview about what had to done, we started laying out a plan on how we would share the task between eachother.
...
\subsection{Week 3}
At this point we felt like we had done enough planning and was quite ready to start coding. Each of us had our tasks and worked on those task seperatly for about a week to get the most essential building stones up and running.\\
...
\subsection{Week 4}
when most of the fundemental part where done we could start coding functionality. A lot of time was spent on including a functionality and then adapting the rest of the code to work with the functionality through a lot of bug testing. We had a list of functions we wanted to implement, so we picked at will what we wanted to do. When we where done with one task, we picked another one.
...
\subsection{Week 5}
Week 5 were mostly spent on finishing up as many functions as we could manage, fixing as many bugs as we could and make the code as efficient as possible.\\

\textbf{An overview over who had the most to do with most of the files:}\\

\begin{tabular}{| l | l | l | l |}
\hline
Tommy 				& Halvor 			& Victor\\ \hline
configurationClass.php		& tvdbClass.php		& activeRecord.php \\
databaseClass.php 			& fileHandlerClass.php 	& channelClass.php \\
index.php				&emailSenderClass.php 	& episodeClass.php\\
userClass.php 			&				& showClass.php\\
userResetPasswordClass.php 	&				& table.php\\
tpbClass.php 			&				& browse.php\\
 					&				& details.php\\						
\hline
\end{tabular}
